---
title: "Graph Individual Well"
author: "Rudolph"
date: "9/16/2019"
output: html_document
---
```{r fig.width=12, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(glue)
library(plotly)
library(scales)
library(htmltools)

wellNumber <- "PH16"
```
## Example for Well `r glue({wellNumber})`

Disclaimer: This is a draft example of displaying a period of record for an individual well at Prisoner's Harbor wetland.  A seperate python script compiles all data for the site into one large csv file, which is the base data for this script. 

**Still to do: some wells have different top of casing readings during certain time frames.  For optimal accuracy, this will need to be incorporated into the script.**

```{r fig.width=12, message=FALSE, warning=FALSE}


wellData <- read_csv("combined_csv.csv", 
    col_types = cols(`Barometric Pressure (PSI)` = col_skip(), 
        `Date and Time` = col_datetime(format = "%m/%d/%Y %H:%M:%S %p"), 
        `Depth (ft)` = col_skip(), 
        Seconds = col_skip(), 
        `Temperature (C)` = col_skip(), 
        `Unnamed: 5` = col_skip(), 
        `Unnamed: 6` = col_skip()))


# Rename the fields
names(wellData) <- c('DateTime', 'PSI', 'Well' )

wellData$Well <- as.factor(wellData$Well)

# Trim out unneeded fields
wellData$Date <- format(wellData$DateTime, "%m-%d-%Y")

wellData$Date<- as.Date(wellData$Date, format="%m-%d-%Y")
str(wellData)
glimpse(wellData)

# Get the stats for each well needed to perform the calculations
well_stats <- read_excel("~/R Projects/Wetland Wells/Well Stats.xlsx")



get_stat <- function(stat){
  return_stat <- well_stats %>% 
  filter(Well == !!wellNumber) %>% 
  pull(stat)
  
  return(return_stat)
}

# Pull stats into variables 
tow <- get_stat("tow")
toc <- get_stat("toc")
dgs <- get_stat("dgs")
fbgs <- get_stat("fbgs")

# Select just the well needed, and perform the calculations into new fields
wellSelect <- wellData %>% 
  filter(Well == wellNumber) %>% 
  mutate(WaterTableElevM = tow-toc+PSI*0.703772,
         GroundSurfaceElev = dgs,
         FtBelowGS = fbgs)

# Narrow down the min and max dates
earliest <- min(wellSelect$Date)
latest <- max(wellSelect$Date)

# Prepare precip data
# Source: http://climateanalyzer.science/python/u_thresh.py?station=santa_cruz_raws&year1=2011&year2=2019&title=Santa%20Cruz%20Island%20automated%20station&lowerthresh=daily&upperthresh=70&station_type=RAWS
precip <- read_csv("~/R Projects/Wetland Wells/santa_cruz_raws_thresholds.csv", 
                   col_types = cols(`Avg. Relative Humidity (%)` = col_skip(), 
                                    `Avg. Wind Speed (MPH)` = col_skip(), 
                                    Date = col_date(format = "%m/%d/%Y"), 
                                    `Tmax (F)` = col_skip(), 
                                    `Tmin (F)` = col_skip(),
                                    X7 = col_skip()))

names(precip) <- c('Date', 'Precip')
precip$Date <- as.POSIXct(precip$Date)

# Trim to min/max dates pulled in from the well data
precip <- precip %>% 
  filter(Date > earliest & Date < latest)

# Make graph to match Joel's excel graph
p <- ggplot(wellSelect, aes(x = DateTime)) +
  geom_line(aes(y=WaterTableElevM, colour = "WaterTableElevM"), size=.5, alpha=0.6) +
  geom_line(aes(y=GroundSurfaceElev, colour = "GroundSurfaceElev"), size=.6, alpha=0.6, ) +
  geom_line(aes(y=FtBelowGS, colour = "FtBelowGS"), size=.6, alpha=0.6, linetype = "longdash") +
  # scale_x_date(date_breaks = "2 month", date_labels =  "%b %Y") +
   scale_x_datetime(labels = date_format("%Y-%m-%d"),
                     date_breaks = "730 hours") +
  theme(axis.text.x=element_text(angle=60, hjust=1), legend.position="bottom") +
  ggtitle(glue("Prisoners Wetland Well {wellNumber} Readings {earliest} to {latest}"), subtitle =  "Height of water above sensor (meters)") + 
  xlab("Date and Time") +
  ylab("Meters above Sensor") + 
  scale_colour_manual("", values = c("WaterTableElevM"="black", "GroundSurfaceElev"="darkgreen",  "FtBelowGS"="blue"))  +
  geom_bar(data=precip, aes(x=Date, y=Precip), stat="identity", fill="tan1", colour="sienna3") +
  scale_y_continuous( "meters",  sec.axis = sec_axis(~ . * 1, name = "inches"))

# Make an interactive graph
ggplotly(p)


```
